---
title: "Evaluating Candidate Models"
author: "Steph Locke"
date: "17 February 2017"
output: html_document
---

We can gather up all our predicted values.
```{r cols}
trainres<-data.frame(
  actual=titanic_train_c$survived,
  allin=predict(allin,titanic_train_c),
  simple=predict(simple,titanic_train_c),
  net=predict(net,titanic_train_c),
  boosted=predict(boosted,titanic_train_c),
  allinval=predict(allin,titanic_train_c,type = "prob"),
  simpleval=predict(simple,titanic_train_c,type = "prob"),
  netval=predict(net,titanic_train_c,type = "prob"),
  boostedval=predict(boosted,titanic_train_c,type = "prob")
)

titanic_test_c_na<-na.omit(titanic_test_c)
testres<-data.frame(
  actual=titanic_test_c_na$survived,
  allin=predict(allin,titanic_test_c_na),
  simple=predict(simple,titanic_test_c_na),
  net=predict(net,titanic_test_c_na),
  boosted=predict(boosted,titanic_test_c_na),
  allinval=predict(allin,titanic_test_c_na,type = "prob"),
  simpleval=predict(simple,titanic_test_c_na,type = "prob"),
  netval=predict(net,titanic_test_c_na,type = "prob"),
  boostedval=predict(boosted,titanic_test_c_na,type = "prob")
)
```

## Confusion Matrices

### allin
```{r cmallin}
confusionMatrix(trainres$actual, trainres$allin)
confusionMatrix(testres$actual, testres$allin)
```
### simple
```{r cmsimple}
confusionMatrix(trainres$actual, trainres$simple)
confusionMatrix(testres$actual, testres$simple)
```

### glmnet
```{r cmnet}
confusionMatrix(trainres$actual, trainres$net)
confusionMatrix(testres$actual, testres$net)
```

### gbm
```{r cmboosted}
confusionMatrix(trainres$actual, trainres$boosted)
confusionMatrix(testres$actual, testres$boosted)
```

## Gini and AUC

### allin
```{r gallin}
library(optiRum)
  giniChart(trainres$allinval.Survived,trainres$actual)
  giniChart(testres$allinval.Survived,testres$actual)
```

### simple
```{r gsimple}
  giniChart(trainres$simpleval.Survived,trainres$actual)
  giniChart(testres$simpleval.Survived,testres$actual)
```

### glmnet
```{r gnet}
  giniChart(trainres$netval.Survived,trainres$actual)
  giniChart(testres$netval.Survived,testres$actual)
```

### gbm
```{r gboosted}
  giniChart(trainres$boostedval.Survived,trainres$actual)
  giniChart(testres$boostedval.Survived,testres$actual)
```

## Selecting a model
We can discard the simple model - it doesn't give sufficient discrimination compared to the other models.


The full GLM and the regularized version, look like they have similar levels of discrimination. We could do a tuning exercise on the regularized model to see if we could improve it. Given time constraints, we will use the full GLM.

The gradient boosted model appears to be performing best.

## Future work
We could further tune models and remove unimportant variables.

In other situations, we could compare against another out of time sample.
